---
title: "PA-1"
output: html_document
date: '2022-07-19'
---

Setting default options por knitr
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Opening libraries needed
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
```


### 1. Code for reading in the dataset and/or processing the data
```{r}
data_na<-read.csv2("C:/Users/spars/Downloads/repdata_data_activity/activity.csv", sep = ",")
data <- na.omit(data_na)
head(data)
```

### 2. Histogram of the total number of steps taken each day

```{r}
data_sum<-data %>%                                   # Specify data frame
  group_by(date) %>%                             # Specify group indicator
  summarise_at(vars(steps),                      # Specify column
               list(total_steps = sum))                # Specify function
ggplot(data_sum,aes(date,total_steps)) + 
  geom_bar(stat="identity", fill= data_sum$total_steps ) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
### 3. Mean and median number of steps taken each day
```{r}
mean <- mean(data$steps)
medi <- median(data$steps)
```
The Mean number of steps taken each day is `r mean`. 
The Median number of steps taken each day is `r medi`.


### 4. Time series plot of the average number of steps taken
```{r}
data_mean <- data %>%
    group_by(date) %>%
    summarize(steps_mean = mean(steps, na.rm=TRUE))  
ggplot(data_mean, aes(date, steps_mean, group = 1)) +
         geom_line() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r}
mean_interval<- data %>%
    group_by(interval) %>%
    summarize(steps_mean = mean(steps, na.rm=TRUE))  
maxmean_interval = mean_interval$interval [which.max(mean_interval$steps_mean)]
```
The 5-minute interval that, on average, contains the maximum number of steps is `r maxmean_interval`. 


### 6. Code to describe and show a strategy for imputing missing data
```{r}
data_input <- data_na %>% 
  group_by(interval) %>% 
  mutate(steps = ifelse(is.na(steps), 
                            mean(steps, na.rm = TRUE), 
                            steps))
head(data_input)
```

### 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r}
data_inputDate <- data_input %>%
    ungroup()%>%
    group_by(date) %>%
    summarize(steps_mean = mean(steps, na.rm=TRUE))
ggplot(data_inputDate, aes(date, steps_mean, group = 1)) +
         geom_line() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
data_input$dateType <-  ifelse(as.POSIXlt(data_input$date)$wday %in% c(0,6), 'weekend', 'weekday')
ggplot(data_input, aes(interval, steps)) + 
    geom_line() + 
    facet_grid(dateType ~ .) +
    xlab("5-minute interval") + 
    ylab("avarage number of steps")
```

All of the R code needed to reproduce the results (numbers, plots, etc.) in the report